Physical structure of an environment and microbial biomass composition variability affect the performance of microbially explicit model

### 2021-03-19 SI_code_2019.Rmd
reorg files for 2021 reanalysis

---
title: Towards more realistic model representation of microbial population dynamics in complex environment
author: "Petr Capek, Katherine Todd-Brown, Natalie Sadler, Michal Choma, Jianqiu Zheng, Nancy Hess, Kirsten Hofmockel"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

>>>>

---
title: Physical structure of an environment and microbial biomass composition variability affect the performance of microbially explicit model
author: "Petr Capek, Katherine Todd-Brown, Natalie Sadler, Michal Choma, Jianqiu Zheng, Nancy Hess, Kirsten Hofmockel"
date: "`r Sys.Date()`"
output: html_document
editor_options:
  chunk_output_type: console
---
